Union and intersection contracts are hard, actually

### 2021-09-15 paper.tex
Update paper.tex
Co-authored-by: Arnaud Spiwack <arnaud.spiwack@tweag.io>

Union contracts are different. Consider the program presented in
Figure~\ref{fig:wrong-union-function}. The same \nickel{f} is now given a union
contract. \nickel{f} is violating this contract once again, as it neither maps
positive numbers to positive numbers nor positive numbers to non positive numbers.

>>>>

Union contracts are different. Consider the program presented in
Figure~\ref{fig:wrong-union-function}. The same \nickel{f} is now given a union
contract. \nickel{f} is violating this contract once again, as it neither maps
positive numbers to positive numbers nor positive numbers to nonpositive numbers.
